---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# openaccess

<!-- badges: start -->
<!-- badges: end -->

openaccess provides a simple check of [open access](https://en.wikipedia.org/wiki/Open_access) for scientific papers. The only data required is a DOI. The list of supported journals grows steadily, see below for the current list of verified sources.

## Installation

You can install the development version of openaccess from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("ErdaradunGaztea/openaccess")
```

## How to use

You'd most often check the open access status by passing the DOI.

```{r with_doi, cache=TRUE}
library(openaccess)
is_open_access("10.1093/nar/gkac882")
```

However, if you already have a HTML content, there's no point in extracting the DOI to download the site again.

```{r with_html, cache=TRUE}
site <- rvest::read_html("https://academic.oup.com/nar/article/51/D1/D352/6761729")
is_open_access(site)
```

## Verified journals

The following journals were validated against the solution and split into two groups: supported and unsupported (at least for the time being).

### Supported sources

* [Academic Press](https://www.elsevier.com/books-and-journals/academic-press)
* [Biophysical Journal](https://www.sciencedirect.com/journal/biophysical-journal)
* [eLife](https://elifesciences.org)
* [Elsevier](https://www.elsevier.com)
* [Frontiers](https://www.frontiersin.org)
* [Journal of Biological Chemistry](https://www.jbc.org)
* [Journal of Neuroscience](https://www.jneurosci.org)
* [MDPI](https://www.mdpi.com)
* [Nature](https://www.nature.com)
* [OUP Academic](https://academic.oup.com)
* [PLOS ONE](https://journals.plos.org/plosone/)
* [Portland Press](https://portlandpress.com)
* [The Royal Society of Chemistry](https://www.rsc.org)
* [SpringerLink](https://link.springer.com)

### (Confirmed) unsupported sources

The following sites return 403 or 503 code upon accessing; hopefully a workaround will be implemented in the future versions of openaccess.

* [ACS Publications](https://pubs.acs.org)
* [Analytical Science Journals](https://analyticalsciencejournals.onlinelibrary.wiley.com)
* [FEBS Press](https://febs.onlinelibrary.wiley.com)
* [PNAS](https://www.pnas.org)
* [Science](https://www.science.org)
* [Wiley Online Library](https://onlinelibrary.wiley.com)

## End notes

I believe in equal rights and treatment for everybody, regardless of their sexuality, gender identity, skin tone, nationality, and other features beyond human control. Thus, I do not allow openaccess to be used in any project that promotes hate based on the aforementioned factors.
